(tentative) Rotational Spectral Unmixing of Exoplanets

### 2017-02-13 paper/main.tex
further updating...(but halfway)

In this section, we discuss the general framework to analyze the diurnal light curves, and present some demonstrations using the mock data created in Section \ref{s:mockdata}.

@@

@@

A question is whether the above formulation leads us to a unique solution of either $\{ {\bf \fast},\,{\bf s} \}$ or $\{ {\bf f},\,{\bf s}\}$, given the data matrix, ${\bf d}$.

Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J-$th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the hyperplane defined by $K$ ($<J$) number of points, $\{{\bf s}_k\} $ and are enclosed by $\{{\bf s}_k \}$. \memoYF{How is it called in one word in mathematics?}\ 
Conversely, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subjected to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), and the associated matrix, $\fast _{ik}$, can always be found. 
Additional constraint comes from the condition (\ref{eq:tilde_s_range}). This limits the range where $\{ {\bf s}_k \}$ can exist, but in general this is not sufficient to result in a unique solution. 
Therefore, predicting ${\bf \fast }$ and ${\bf s}$ from ${\bf d}$ is clearly a ill-posed problem.

>>>>

In this section, we discuss the general framework to analyze the diurnal light curves, and present some demonstrations using the mock data created in the previous section. 
Sections \ref{ss:model} and \ref{ss:PCplane} are essentially the recapitulation of the previous papers, in particular \citet{Cowan2013} \citep[but see also][]{Cowan2009,Cowan2011,Fujii2010,Fujii2011}.  
We, however, choose to include these discussions as a baseline to establish the later arguments. 
\memoYF{Too many overlaps??}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Principal Component (Hyper-)Plane\\and Graphical Conception}
\label{ss:PCplane}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%A question is whether the above formulation leads us to a unique solution of either $\{ {\bf \fast},\,{\bf s} \}$ or $\{ {\bf f},\,{\bf s}\}$, given the data matrix, ${\bf d}$.

Equation (\ref{eq:tilde_d_f_ast_s}) coupled with the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}) indicates the geometrical relationship among ${\bf d}$, ${\bf \fast }$, and ${\bf s}$ in the $J$-th dimensional space, where $\{{\bf d}_i\}$ correspond to the points that are located on the hyperplane defined by $K$ ($<J$) number of points, $\{{\bf s}_k\} $ and are enclosed by $\{{\bf s}_k \}$. \memoYF{How is it called in one word in mathematics?}\ 
We show this graphically using the mock datasets shown in Section \ref{s:mockdata}.

The original data, however, have 4 photometric bands (i.e., $J=4$), and $J$-th dimensional space is inconvenient for visualization. 
We thus reduce the dimensionality using principal component analysis (PCA). 
Unsurprisingly we extract two dominant principal components (PCs) through PCA (other components have vertually zero contribution), which are presented in Figure \ref{fig:PCs}.

We subtract the 4-band light curves by the time averages of the respective bands, and its trajectory in the PC plane is shown in Figure \ref{fig:trajectory}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tbh!]
    \begin{center}
\includegraphics[width=\hsize]{PCA_V_jn.pdf}
    \end{center}
    \caption{Principal components.}
\label{fig:PCs}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \begin{center}
\includegraphics[width=\hsize]{mockdata_135deg_3types_t12_lc_noreg.png}
    \end{center}
    \caption{Trajectory on the principal component plane.}
    \label{fig:trajectory}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
    \begin{center}
\includegraphics[width=\hsize]{mockdata_135deg_3types_t12_lc_noreg.png}
    \end{center}
    \caption{Trajectory on the principal component plane.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Conversely, {\it any} set of $\{ {\bf s}_k \}$ that enclose the data points $\{{\bf d}_i\}$ in the hyperplane can be a solution of Equation (\ref{eq:tilde_d_f_ast_s}) subjected to the conditions (\ref{eq:tilde_f_range}) and (\ref{eq:tilde_f_sum}), and the associated matrix, $\fast _{ik}$, can always be found. 
Additional constraint comes from the condition (\ref{eq:tilde_s_range}). This limits the range where $\{ {\bf s}_k \}$ can exist, but in general this is not sufficient to result in a unique solution. 
Therefore, predicting ${\bf \fast }$ and ${\bf s}$ from ${\bf d}$ is clearly a ill-posed problem.
